Interaction network structure maximizes community-level plant reproduction success via niche complementarity

### 2019-04-26 paper_round2.Rmd
minor changes to script and inclusion of word documents: paper, cover letter and suppl mat

Ainhoa Magrach, Francisco de Paula [or Curro, ask him]() Molina, Ignasi Bartomeus

@@

Keywords: nestedness, niche complementary, fruitset, pollination, plant-pollinator interaction

@@

Words in Abstract: 147 words

@@

Words in text boxes:

Number of references:

@@

@@

Pollinators provide key services to plants by facilitating pollen flow between individuals. The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010], [@I.2019]) have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].

Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed across different plant individuals. Some have gone a step further by including information on the efficiency of these visits, thus adding a measure of quality to the pollination services [@Willcox2017](I wonder if the preceeding sentence is necesary, given our paper is not about efficiency). Contrastingly, community-level analyses remain scarce [@Bennett2018]. Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species. We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017]. Understanding how changes in pollinator diversity and interaction structure affect whole community assemblages is thus a major challenge that requires attention.

The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level, have done so using mainly experimental setups. As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that community structure had an important effect [@Frund2013]. In particular, these authors found that niche complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013]. This provides added information on the effects of biodiversity for ecosystem functioning, suggesting that not only the diversity of species present but also the diversity of roles and ways in which a community is structured are determinant factors.

Indeed, theoretical research has long suggested that the structure of multitrophic communities has an effect for ecosystem functioning (reviewed in [@Thompson2012]). This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data (but see [@Poisot2013]). Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012]. We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks [@Bascompte2007b] and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016]. Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures [Bascompte et al 2013 PNAS] or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004]. However, how the structure shaping this network of interactions affects key ecosystem functions such as plant reproduction remains untested [@Winfree2013]. The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.

Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously-used simple visitation metrics (e.g., number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success. In addition to average values, we also evaluate whether community structure helps us explain differences in equity in reproductive success across individuals within a species and species within a community as a measure of evenness and stability in the pollination service.

@@

@@

Our study was conducted in SW Spain within the area of influence of Doñana National Park (Figure 1). Here, we surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km). Each site was surveyed 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins. Along each transect, we identified all plant species and recorded all the flower visitors that legitimately visited them during each 30-min period. In addition, in each round we conducted 3 minutes focal observations of 3 individuals belonging to the 19 most common species totalling X census [give mean per site?](Curro). In addition, unrecorded interactions between plant and pollinators during the sampling were recorded when observed out of the timed periods, as this dificult to observe interactions may be important for defining the network structure. Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FdPM with the aid of experts in the different taxonomic groups (see acknowledgements). All surveys were done under similar weather conditions, avoiding windy or rainy days. [maybe say we tried excluding singletons and analysis do not change?]()

@@

Within each site, we marked between `r min(f.inds$tot.inds)` and `r max(f.inds$tot.inds)` individuals (`r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) of `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`), depending on the availability and presence of flowers during the sampling events. For each individual, we counted the number of flowers at each sampling point and recorded fruitset, the number of seeds per fruit (for `r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits, `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`) and average seed weight per fruit at the end of the season. Our survey included a total of `r nlevels(f2$Plant.sp)` different plant species across our `r nlevels(f2$Site_ID)` sites.

**Data analyses**

@@

In order to analyse how differences within the community structure might affect plant reproductive success, we constructed weighted plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling. We thus obtained one weighted interaction network per site, representing the frequency of visits by different pollinator species to different plant species. For each network, we then proceeded to extract a series of relevant network metrics.

@@

At the species level, we focused on attributes defining the position of a focal plant species within the larger community. As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap between a focal plant species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality [is this calculated onto the unipartite plant network? If so explain](), which depicts the [importance](importance can mean anything, can you be more especific?) of the plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness.

@@

Nestedness is the property by which specialists interact with a subset of the species that generalists interact with [@Bascompte2003]. Although there is an ongoing debate in the literature, some studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009]. However, many network attributes vary with network size and complexity [@Bluthgen2006]. In the case of nestedness, we know it can be affected by network size and connectance [@Song2017]. An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks. However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017]. We thus followed the advice provided by Song et al. (2017) by using a normalized value of the widely-used nestedness metric NODF [@Almeida-Neto2011], $NODF_c$. This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance, S is network size and $NODF_n = NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017].[See new paper by Benno simons updating Song method :(]()

Niche complementariety metrics are important because plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]). To calculate niche complmentarity we used a community-level measure defined as the total branch length of a functional dendrogram based on qualitative differences in visitor assemblages between plants [@Devoto2012; @Petchey2007a]. All network metrics were calculated using package bipartite [@Dormann2009].

[Yet at present we do not know how the interplay between redundancy and complementarity in species roles determines reproductive success.](I don't see where to place this sentence. I like it, but was breaking the flow. Discusion?)

@@

In order to evaluate whether adding information on community structure improves our ability to explain differences in reproductive success - both at the species and the community level - we used general linear (GLMs) and general linear mixed models (GLMMs). In both cases (species and community-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2, that additionally included information on community structure.

At the species level, model 1 included as explanatory variables the diversity of pollinator species visiting a focal plant and the total number of visits received by that plant species; while model 2, added the two network attributes calculated at the species level: average niche overlap and centrality. In this case, we included plant species nested within site as a random effect to account for the non-independence of several individuals measured for the same plant species within each site. The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009]. Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita index [@Zhang2016]. As a measure of centrality we used weighted closeness centrality which describes centrality through the path lengths of a species to other species in the network using a weighted representation of the network [@Dormann2009]. Response variables included fruitset for different individuals measured per species analyzed using a binomial distribution, the number of seeds per species for different individuals analyzed using normal distribution and average values per species of fruit and seed weight fitted to poisson distributions.

At the community level, we upscaled our species-level analyses. In this case, model 1 included total pollinator diversity and the total number of visits received by all plants within the community as explanatory variables. Model 2, in turn, added information on community structure by including nestedness and niche complementarity as explanatory variables. As response variable we had the average reproductive success for the whole community (i.e., average fruitset analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight previously scaled for each species for which we used normal distributions). We thus had a single value per site and no random effects are needed in this case.

Average values of reproductive success at the community level can be driven to a large extent by a single plant species. Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community. We therefore calculated a measure of equity in reproductive success at the community level as the proportion of species within a community with normalized [explain how, normalizations usually make 0 centred values, and values above 0.5 makes no sense]() average fruitset values above 0.5. We repeated this using 0.25 and 0.75 thresholds. We then used the same framework as before and fit the same models 1 and 2 GLMs as the ones used at the community level, but using equity in reproductive success as the response variable and a binomial distribution. In this case, we retained only sites for which we had at least measured reproductive success for 2 plant species (N=14 sites). 
We used information criterion methods to find the best model for each case and selected the ones with the lowest Akaike Information Criterion (AIC) value. $\Delta AIC<2$, were not considered enough to select one model over the other [@Burnham2011].

_Simulating the effect of community structure as sample size increases_ [no se si le pondria titulo aparte o no, quizas no hace falta, yo o uniria a estatistical analysis]()

@@

To test this, we ran a simple simulation in which the number of species considered increased at each time step and for each time step we re-calculated equity in reproductive success. Instead of drawing plant species randomly for each run, we tested all possible combinations for each plant number level and network, as the number of combinations is low (e.g. for n = 3 plant selected out of 6 there is only 20 possible combiations). Then, we tested the overall relationship between equity in reproductive success and both community-level network metrics we measured: nestedness and functional complementarity within our simulated communities. To this end, for each species number level considered, we randomly selected one of the generated equity values across each of the 16 communities, regress this against our netrwock level predictors and extracted the model estimates. We averaged all estimates from 1,000 simulated combinations per number of plants considered. We expect that the more plants considered, the larger the resulting average estimates will be. Note that we only interpret the mean effects, as the variance among different plant number of species depends on the initial number of combinations.

@@

Within our sampling we recorded `r nrow(d)` pollinator individuals belonging to `r nlevels(unique(d$Plant_gen_sp))` species of plants and `r nlevels(unique(d$Pollinator_gen_sp))` species of pollinators. Within the pollinator community the distribution in different orders was: `r round(d.order$prop[d.order$order=="Hymenoptera"]*100, digits=2)`% Hymenoptera, `r round(d.order$prop[d.order$order=="Diptera"]*100, digits=2)`% Diptera, `r round(d.order$prop[d.order$order=="Coleoptera"]*100, digits=2)`% Coleoptera, `r round(d.order$prop[d.order$order=="Lepidoptera"]*100, digits=2)`% Lepidoptera, while Araneaeae and Neuroptera represented `r round(d.order$prop[d.order$order=="Araneae"]*100, digits=2)`% each.

@@

Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Figure S1). Our values of sampling completeness are slightly smaller in the case of pollinators probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014a]. [well, and the fact that we added "outs", which are singletons, a key piece used by Chao estimators!, SHould we mention this?]()

@@

At the species level, in the case of fruitset, our results show that model 2 is the best model explaining the variability observed. In this case, we find a positive effect of pollinator species diversity (measured using the species´normalised degree, Fig. 2) as well as a positive effect of the centrality of the focal plant on its fruitset (Fig. 2). [to what extent ND is a network level metric i.e. not a simple metric like number of links¿? I am playing devils advocate here.]()

@@

# extract coefficients and p-values for m2 and present them in paper
coefs.m2 <- data.frame(coef(summary(m2)))
coefs.m2
Table1<-round(coefs.m2[,1:3],digits=2)
rownames(Table1)<-c("(Intercept)", "Normalized degree", "Total number of visits", "Weighted closeness", "Niche overlap")
#at the end of the paper

@@

For the number of seeds per fruit, our results show that both model 1 and model 2 are equally good in explaining the variability observed (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other. Given that model 2 has a greater number of variables which should be penalized given the added complexity it provides, we will comment results only for model 2. In this case, we find a positive effect of the niche overlap between plant species (Fig. 3).

@@

# extract coefficients and p-values for m1 and present them in paper
coefs.m2.seed <- data.frame(coef(summary(m2.seed)))
# use normal distribution to approximate p-value
#coefs.m2.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m2.seed$t.value)))
coefs.m2.seed
Table2<-round(coefs.m2.seed,digits=2)
rownames(Table2)<-c("(Intercept)", "Normalized degree", "Total number of visits", "Weighted closeness", "Niche overlap")

@@

Figure3<-ggplot(m2.seed@frame,  aes(x=m2.seed@frame$niche.overlap.sc, y=y_partial_norm_seed_inv, color= Plant.sp)) +    
  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
  xlab("Niche overlap") +      
  ylab("Seeds per fruit") + theme_bw()  + theme (legend.position= "bottom") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"))

@@

For all other measures of reproductive success considered (i.e., fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, pollinator species diversity and the total number of visits received by a focal plant species). However, none of the variables included within our model explain the differences observed.

@@

# extract coefficients and p-values for m1 and present them in paper
tableS4<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
rownames(tableS4)<-c("(Intercept)", "Normalized degree", "Total number of visits")

@@

# extract coefficients and p-values for m1 and present them in paper
tableS5<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)
rownames(tableS5)<-c("(Intercept)", "Normalized degree", "Total number of visits")

@@

At the community level, we find different patterns for fruitset and the number of seeds per fruit as compared to those for fruit and seed weight. In the case of fruitset and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$). Again, because this suggests model 2 is a good model despite its added complexity, we will comment results for this model only. In particular, we find that both fruitset and the number of seeds per fruit are positively related to niche complementarity between pollinators (Fig. 4). Additionally, we find a negative effect of community-level pollinator species diversity and the total number of visits on average fruitset (Fig. 4).

@@

```
Figure X. Results of simulation evaluating the importance of niche complementarity in determining differences in equity in reproductive across communities harboring from one to six species. Points represent average values for 16 combinations of XXXX 100 times??? [can you fill this Nacho?]()

@@

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5, fig.width=8}

>>>>

Ainhoa Magrach^1^, Francisco P. Molina^2^, Ignasi Bartomeus^2^

@@

^1^Basque Centre for Climate Change-BC3, Edif. Sede 1, 1º, Parque Científico UPV-EHU, Barrio Sarriena s/n, 48940, Leioa, Spain

^2Estación Biológica de Doñana (EBD-CSIC), Avda. Américo Vespucio 26, Isla de la Cartuja, 41092, Sevilla, Spain

@@

Words in Abstract: 148 words

@@

Number of references: 45

@@

Keywords: nestedness, niche complementary, fruitset, pollination, plant-pollinator interactions

@@

Pollinators provide key services to plants by facilitating pollen flow between individuals. The recent declining trends found for some pollinator species in some regions of the planet ([@Potts2010; @I.2019]) have led many researchers to focus on the functional impacts of these changes in pollinator diversity, with a major focus being placed on the consequences for plant reproductive success [@Biesmeijer2006].

  Many research efforts have targeted the reproductive success of individual plant species [@Albrecht2012a; @doi:10.1111/1365-2745.13055], and used relatively simple visitation metrics (e.g., the number of pollinator species that visit a plant or the number of visits they perform) to explain the differences observed across different plant individuals. Contrastingly, community-level analyses remain scarce [@Bennett2018]. Yet plants and pollinators do not interact in isolation, but rather are embedded within larger networks of interactions encompassing other plant and pollinator species. We are thus missing an important part of the picture, which includes the direct interactions between the whole ensemble of plants and pollinators, but also the indirect ones between species within one guild (e.g., plants) through their shared resources [@Carvalheiro2014; @Lazaro2014; @Mayfield2017]. Understanding how changes in pollinator diversity and interaction structure affect whole community assemblages is thus a major challenge that requires attention.

  The few pollination studies that have analysed the effects of changing pollinator diversity for reproductive success at the community level have done so using mainly experimental setups. As an example, a study that experimentally recreated a plant community with 9 plant species and differing levels of pollinator diversity across different enclosures, found that not only pollinator species diversity had an effect for average reproductive success, but also they found that community structure had an important effect [@Frund2013]. In particular, these authors found that niche complementarity between pollinators, in terms of plant species and temperature coverage (a measure of the overlap in the use of plant resources and optimum temperature activity) had a positive effect for average seed set at the community level [@Frund2013]. This provides added information on the effects of biodiversity for ecosystem functioning, suggesting that not only the diversity of species present, but also the diversity of roles and ways in which a community is structured, are determinant factors.

  Indeed, theoretical research has long suggested that the structure of multitrophic communities has an effect for ecosystem functioning (reviewed in [@Thompson2012]). This line of research, primarliy driven by food-web studies, has greatly advanced theory, but these ideas have not yet been tested using empirical data (but see [@Poisot2013]). Specifically, a major knowledge gap resides in understading which aspects of structure determine which aspects of function [@Thompson2012]. We are now at a point in which there is considerable understanding on the attributes characterizing mutualistic interaction networks [@Bascompte2007b] and we have a substantial understanding of how these attributes vary along different types of gradients [@Pellissier2017; @Tylianakis2016]. Especially, in the case of pollination, we have ample knowledge on the attributes that shape these mutualistic interactions at the community level, such as a prevalence of nested structures [@Bascompte2003] or the presence of asymmetric specialization as a pervasive feature [@Vazquez2004]. However, the pathways by which the structure of these networks of interactions affect key ecosystem functions such as plant reproduction remain to be understood [@Winfree2013]. The time is thus ripe to use this knowledge to explore relationships between community structure and ecosystem functioning, with special emphasis being placed on the underlying mechanisms that drive these relationships.

  Here, we present one of the first efforts linking pollinator visitation and plant reproductive success at the community level. To this end, we use a well-replicated dataset encompassing 16 well-resolved plant-pollinator interaction networks coupled with data on the reproductive success of 19 plant species recorded at Mediterranean shrub ecosystems within the area of influence of Doñana National Park in SW Spain. Our study focuses on understanding whether adding information on the structure of the community to previously used simple visitation metrics (e.g., the number and diversity of pollinator species visiting a plant species) aids in better explaining the differences observed in community-wide reproductive success. In doing so, we conducted our analyses focusing on reproductive success at two different levels: (i) at the species level by considering the effect of the position of a focal species within the larger network and its impact on its individual reproductive success, and (ii) at the community level, by evaluating how attributes that describe the whole community might affect average values of reproductive success. In addition to average values, we also evaluate whether community structure helps us explain differences in equity in reproductive success across species within a community, as a measure of evenness and stability in the pollination service.

@@

#check number of sps per site surveyed in the focal analyses

foc<-subset(d, d$Out=="focal")
foc2<-ddply(foc, c("Site_ID", "Plant_gen_sp"), summarise, 
              tot.species = length(Plant_gen_sp)) #number of species per site
foc3<-ddply(foc2, c("Site_ID"), summarise, 
            tot.species = length(Site_ID)) #number of species per site

@@

Our study was conducted in SW Spain within the area of influence of Doñana National Park (Fig. 1). Here, we surveyed 16 Mediterranean woodland patches with an average distance of 7 km between them (min= 3 km, max= 46.5 km). Each site was surveyed 7 times during the flowering season of 2015 (from February to May) following a 100-m x 2 m transect for 30 mins. Along each transect, we identified all plant species and recorded all the flower visitors that legitimately visited them during each 30-min period. In addition, at each round we conducted 3 minutes of focal observations on 3 individuals per species belonging to the 19 most common species across the study area (`r round(mean(foc3$tot.species), digits=2)` $\pm$ `r round(sd(foc3$tot.species), digits=2)` species per site). Furthermore, we included some interactions between plant and pollinator individuals that were not observed during the sampling but that were seen immediately after, as some of these interactions are difficult so see and might be important to define network structure. Floral visitors (from now on referred to as pollinators) that could not be identified in the field were captured, stored and identified in the laboratory by FPM with the aid of experts in the different taxonomic groups (see acknowledgements). All surveys were done under similar weather conditions, avoiding windy or rainy days.

@@

Within each site, we marked between `r min(f.inds$tot.inds)` and `r max(f.inds$tot.inds)` individuals (`r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`), depending on the availability and presence of flowers during the sampling events. For each individual, we counted the number of flowers at each sampling point and recorded fruitset, the number of seeds per fruit (for `r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits, `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`) and average seed weight per fruit at the end of the season. Our survey included a total of `r nlevels(f2$Plant.sp)` different plant species across our `r nlevels(f2$Site_ID)` sites.

_Data analyses_

@@

  In order to analyse how differences in community structure might affect plant reproductive success, we constructed weighted plant-pollinator interaction networks by pooling the data for the 7 rounds of sampling. We thus obtained one weighted interaction network per site, representing the frequency of visits by different pollinator species to different plant species. For each network, we then proceeded to extract a series of relevant network metrics at the species and community levels.

@@

At the species level, we focused on attributes defining the position of a focal plant species within the larger community. As such, we considered two metrics providing complementary non-redundant information: (i) average niche overlap between a focal plant species and other plant species in the community, which covers the potential indirect interactions between different plant species through shared resources (in this case pollinators), and (ii) centrality, which depicts the importance of the role played by a plant species within the larger community (as resource for a large number of pollinator species) and its contribution to network cohesiveness. Centrality represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network, where links between plant species represent shared pollinator species. As a measure of centrality we used weighted closeness centrality, which represents the number of shortest paths going through a focal plant based on a unipartite projection of the bipartite plant-pollinator network using a weighted representation of the network [@Dormann2009]. Here, links between plant species represent shared pollinator species.
  Niche overlap was calculated as the average overlap in pollinator species visiting a focal plant and each of the other plants in the community using the Morisita index [@Zhang2016].

@@

  Nestedness is the property by which specialists interact with a subset of the species that generalists interact with [@Bascompte2003]. Although there is an ongoing debate in the literature, some studies have found that nested networks are more stable and resilient to perturbations because nestedness promotes a greater diversity by minimizing competition among species in a community [@Bastolla2009]. However, many network attributes vary with network size and complexity [@Bluthgen2006]. In the case of nestedness, we know it can be affected by network size and connectance [@Song2017]. An approach that is often used to correct for this, is to use null models and to compare null-model corrected nestedness values across different networks. However, this approach has been recently shown to present the same issues, as z-scores also change with network size and connectance [@Song2017]. We thus followed the advice provided by Song et al. (2017) by using a normalized value of the widely-used nestedness metric NODF [@Almeida-Neto2011], $NODF_c$. This normalized value is calculated as $NODF_c = NODF_n/(C * log(S))$, where C is connectance, S is network size and $NODF_n = NODF/max(NODF)$, which is independent of network size and thus comparable across different networks [@Song2017].

  Niche complementariety metrics are important because plant reproductive success depends on the delivery of conspecific pollen and thus of a certain level of specialization or niche divergence (reviewed in [@Brosi2016]). To calculate niche complmentarity, we used a community-level measure defined as the total branch length of a functional dendrogram based on qualitative differences in visitor assemblages between plants [@Devoto2012; @Petchey2007a]. All network metrics were calculated using package bipartite [@Dormann2009].

  All of these metrics were calculated using all the data as well as for the subset of the data excluding interactions observed outside of sampling periods. Differences between results are minimal for both and thus we will only present results for the analysis using the full dataset.

@@

In order to evaluate whether adding information on community structure improves our ability to explain differences in reproductive success - both at the species and the community level - we used general linear (GLMs) and general linear mixed models (GLMMs). In both cases (species and community-level models) we fit two types of models: (i) model 1, that only included simple visitation metrics and (ii) model 2 that additionally included information on community structure.

  At the species level, model 1 included as explanatory variables the diversity of pollinator species visiting a focal plant and the total number of visits received by that plant species; while model 2, added the two network attributes calculated at the species level: average niche overlap and centrality. In this case, we included plant species nested within site as a random effect to account for the non-independence of several individuals measured for the same plant species within each site. The diversity of pollinator species visiting a focal plant was approximated using the plant´s normalised degree, i.e., the number of links with different pollinator species a plant has, scaled by the number of possible partners [@Dormann2009]. Response variables included fruitset for different individuals measured per species analyzed using a binomial distribution, the number of seeds per species for different individuals analyzed using a normal distribution and average values per species of fruit and seed weight fitted to poisson distributions.

  At the community level, we upscaled our species-level analyses. In this case, model 1 included total pollinator diversity and the total number of visits received by all plants within the community as explanatory variables. Model 2, in turn, added information on community structure by including nestedness and niche complementarity as explanatory variables. As response variable we had the average reproductive success for the whole community (i.e., average fruitset analyzed using a binomial distribution, average number of seeds per fruit and average fruit and seed weight previously scaled, for each species for which we used normal distributions). We thus had a single value per site and no random effects are needed in this case.

  Average values of reproductive success at the community level can be driven to a large extent by a single plant species. Yet, what will determine the persistence of a diverse plant community, is the presence of some sort of “equity” or evenness in reproductive success across the whole community. We therefore calculated a measure of equity in reproductive success at the community level as the proportion of species within a community with normalized [explain how, normalizations usually make 0 centred values, and values above 0.5 makes no sense]() average fruitset values above 0.5. We repeated this using 0.25 and 0.75 thresholds. We then used the same framework as that used for species and community-level analyses and fit the same models 1 and 2 GLMs, but using equity in reproductive success as the response variable fitting a binomial distribution. In all cases, we used information criterion methods to find the best model and selected the ones with the lowest Akaike Information Criterion (AIC) value. Whenever the difference between the AIC of both models was < 2 ($\Delta AIC<2$), we considered that both models were equally good [@Burnham2011].

@@

  To test this, we ran a simple simulation in which the number of species considered increased at each time step and for each time step we re-calculated equity in reproductive success. Instead of drawing plant species randomly for each run, we tested all possible combinations for each plant number level and network, as the number of combinations is low (e.g. for n = 3 plant selected out of 6 there is only 20 possible combiations). Then, we tested the overall relationship between equity in reproductive success and functional complementarity (given its importance in determining differences in reproductive success, see Results section) within our simulated communities. To this end, for each species number level considered, we randomly selected one of the generated equity values across each of the 16 communities, regressed this against our network level predictor and extracted the model estimates. We averaged all estimates from 1,000 simulated combinations per number of plants considered. We expect that the more plants considered, the larger the resulting average estimates will be. Note that we only interpret the mean effects, as the variance among different plant number of species depends on the initial number of combinations.

@@

Within our sampling we recorded `r nrow(d)` pollinator individuals belonging to `r nlevels(unique(d$Plant_gen_sp))` species of plants and `r nlevels(unique(d$Pollinator_gen_sp))` species of pollinators. Within the pollinator community the distribution in different orders was: `r round(d.order$prop[d.order$order=="Hymenoptera"]*100, digits=2)`% Hymenoptera, `r round(d.order$prop[d.order$order=="Diptera"]*100, digits=2)`% Diptera, `r round(d.order$prop[d.order$order=="Coleoptera"]*100, digits=2)`% Coleoptera, `r round(d.order$prop[d.order$order=="Lepidoptera"]*100, digits=2)`% Lepidoptera, while Araneaeae and Neuroptera representing `r round(d.order$prop[d.order$order=="Araneae"]*100, digits=2)`% each.

@@

  Our sampling completeness analyses revealed that with our survey we were able to capture 18-62% of pollinator species (average= 35%), 47-98% for plant species (average= 78%) and 13-41% for plant-pollinator links (average=27%), in line with that obtained with other studies (e.g., [@Chacoff2012], Fig. S1). Our values of sampling completeness are slightly smaller in the case of pollinators, probably as a consequence of the great diversity found in the Mediterranean region and within our study area in particular, a hotspot of insect diversity [@Nieto2014a]. In addition, the fact that we include rare interactions observed outside of our main sampling, or singletons, might also be affecting our results.

@@

At the species level, in the case of fruitset, our results show that model 2 is the best model explaining the variability observed. In this case, we find a positive effect of a simple visitation metric, pollinator species diversity (measured using the species´normalised degree, Fig. 2) as well as a positive effect of a community structure metric, the centrality of the focal plant on its fruitset (Table 1, Fig. 2).

@@

# extract coefficients and p-values for m2 and present them in paper
coefs.m2 <- data.frame(coef(summary(m2)))
coefs.m2
Table1<-round(coefs.m2[,1:3],digits=2)
rownames(Table1)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")
#at the end of the paper

@@

  For the number of seeds per fruit, our results show that both model 1 and model 2 are equally good in explaining the variability observed (i.e.,$\Delta AIC<2$), and therefore we cannot select one over the other. Given that model 2 has a greater number of variables which should be penalized given the added complexity it provides, we will comment results only for model 2. In this case, we find a positive effect of the niche overlap between plant species (Table 2, Fig. 3).

@@

# extract coefficients and p-values for m1 and present them in paper
coefs.m2.seed <- data.frame(coef(summary(m2.seed)))
# use normal distribution to approximate p-value
#coefs.m2.seed$p.z <- 2 * (1 - pnorm(abs(coefs.m2.seed$t.value)))
coefs.m2.seed
Table2<-round(coefs.m2.seed,digits=2)
rownames(Table2)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits", "Centrality", "Niche overlap")

@@

Figure3<-ggplot(m2.seed@frame,  aes(x=m2.seed@frame$niche.overlap.sc, y=y_partial_norm_seed_inv, color= Plant.sp)) +    
  geom_point(size=2.5, shape=21, colour="black", aes(fill=factor(Plant.sp))) + stat_smooth(method=lm,  size=1, se=TRUE, color = "black", alpha=0.4) + 
  #geom_smooth(method=lm, linetype= "dashed", size=0.7, se=FALSE, alpha=0.8) +
  xlab("Niche overlap") +      
  ylab("Seeds per fruit") + theme_bw()  + theme (legend.position= "right") +
  theme(text = element_text(size = 18), axis.text=element_text(size=rel(1)), axis.title=element_text(size=rel(1.3), face="bold")) + 
  scale_fill_discrete(name="Plant species") +  theme(legend.text = element_text(size = 6, face = "italic"), legend.title = element_text(size=11, face = "bold"))

@@

  For all other measures of reproductive success considered (i.e., fruit and seed weight), the best model based on its AIC value was model 1, i.e., the model that only included simple visitation metrics (in this case, pollinator species diversity and the total number of visits received by a focal plant species). However, none of the variables included within our model explain the differences observed (Tables S4-S5).

@@

# extract coefficients and p-values for m1 and present them in paper
tableS4<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
rownames(tableS4)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")

@@

# extract coefficients and p-values for m1 and present them in paper
tableS5<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)
rownames(tableS5)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")

@@

At the community level, we find different patterns for fruitset and the number of seeds per fruit as compared to those for fruit and seed weight. In the case of fruitset and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed (i.e.,$\Delta AIC<2$). Again, because this suggests model 2 is a good model despite its added complexity, we will comment results for this model only. In particular, we find that both fruitset and the number of seeds per fruit are positively related to niche complementarity between pollinators (Tables 3-4, Fig. 4). Additionally, we find a negative effect of community-level pollinator species diversity and the total number of visits on average fruitset (Table 3, Fig. 4).

@@

@@

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=7, fig.width=9}
